Fernando LOOCV

### 2016-10-21 reports/agronomic_data.Rmd
remove code boxes from report

# Agronomic Data
```{r echo = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "knitr", "tibble")

knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = "~/gamazon/",
                     inline = TRUE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, 
                      warning = FALSE, echo = FALSE)
```

@@

# Prepare agronomic data.
genos <- readRDS("./data/processed/common_genotypes.RDS")
hybrid <- genos$Hybrid
all_pheno <- pheno %>%
  rename(Observed = EST) %>%
  as_data_frame() %>%
  filter(G %in% hybrid) %>%
  select(G, Observed, Trait) %>%
  filter(Trait != "ADL") %>%
  mutate(Trait = fct_recode(Trait, 
    "FAT" = "FETT",
    "DMY" = "GTM",
    "DMC" = "GTS",
    "PRO" = "RPR",
    "SUG" = "XZ"),
         Trait = fct_relevel(Trait, 
    c("DMY", "DMC", "ADF", "FAT", "PRO", "STA", "SUG")
    ))

# Select hybrids for which both parents have genomic as well as transcriptomic
# records.
dent <- genos$Dent$mrna
flint <- genos$Flint$mrna
hybrid <- genos$Hybrid %>%
  as_data_frame() %>%
  separate(value, into = c("DF", "Dent", "Flint")) %>%
  mutate(Avail_Dent = ifelse(Dent %in% dent, yes = 1, no = 0),
         Avail_Flint = ifelse(Flint %in% flint, yes = 1, no = 0),
         Tested_Parents = Avail_Dent + Avail_Flint) %>%
  filter(Tested_Parents == 2) %>%
  unite(Hybrid, DF, Dent, Flint) %>%
  .$Hybrid

>>>>

# Agronomic Data
```{r echo = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "knitr", "tibble", "purrr")

knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, 
                      warning = FALSE, echo = FALSE)
```

@@

# Prepare agronomic data.
genos <- readRDS("./data/processed/common_genotypes.RDS")
hybrid <- genos %>%
  filter(Data_Type == "agro", Pool == "Hybrid") %>%
  .$G
all_pheno <- pheno %>%
  rename(Observed = EST) %>%
  as_data_frame() %>%
  filter(G %in% hybrid) %>%
  select(G, Observed, Trait) %>%
  filter(Trait != "ADL") %>%
  mutate(Trait = fct_recode(Trait, 
    "FAT" = "FETT",
    "DMY" = "GTM",
    "DMC" = "GTS",
    "PRO" = "RPR",
    "SUG" = "XZ"),
         Trait = fct_relevel(Trait, 
    c("DMY", "DMC", "ADF", "FAT", "PRO", "STA", "SUG")
    ))

# Select hybrids for which both parents have genomic as well as transcriptomic
# records.
mrna_inbreds <- genos %>%
  filter(Pool != "Hybrid", Data_Type == "mrna") %>%
  split(.$Pool) %>%
  map("G")
hybrid <- hybrid %>%
  as_data_frame() %>%
  separate(value, into = c("DF", "Dent", "Flint")) %>%
  mutate(Avail_Dent = ifelse(Dent %in% mrna_inbreds$Dent, yes = 1, no = 0),
         Avail_Flint = ifelse(Flint %in% mrna_inbreds$Flint, yes = 1, no = 0),
         Tested_Parents = Avail_Dent + Avail_Flint) %>%
  filter(Tested_Parents == 2) %>%
  unite(Hybrid, DF, Dent, Flint) %>%
  .$Hybrid

### 2016-10-21 reports/data_overview.Rmd
remove code boxes from report

knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = "~/gamazon/",
                     inline = TRUE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 6,
                      warning = FALSE, echo = FALSE)
```

@@

full_hybrid <- genos$Hybrid
all_pheno <- pheno %>%
  rename(Observed = EST) %>%
  as_data_frame() %>%
  filter(G %in% full_hybrid) %>%
  dplyr::select(G, Observed, Trait) %>%
  filter(Trait != "ADL") %>%
  mutate(Trait = fct_recode(Trait, 
    "FAT" = "FETT",
    "DMY" = "GTM",
    "DMC" = "GTS",
    "PRO" = "RPR",
    "SUG" = "XZ"),
         Trait = fct_relevel(Trait, 
    c("DMY", "DMC", "ADF", "FAT", "PRO", "STA", "SUG")
    ))
traits <- all_pheno %>%
  .$Trait %>%
  levels()

# Hybrids of parents with records for both endophenotypes
red_dent <- Reduce(intersect, genos[["Dent"]][c("snp", "mrna")])
red_flint <- Reduce(intersect, genos[["Flint"]][c("snp", "mrna")])
red_hybrid <- genos$Hybrid %>%
  as_data_frame() %>%
  separate(value, into = c("DF", "Dent", "Flint")) %>%
  mutate(Avail_Dent = ifelse(Dent %in% red_dent, yes = 1, no = 0),
         Avail_Flint = ifelse(Flint %in% red_flint, yes = 1, no = 0),
         Tested_Parents = Avail_Dent + Avail_Flint) %>%
  filter(Tested_Parents == 2) %>%
  unite(Hybrid, DF, Dent, Flint) %>%
  .$Hybrid
full_hybrid <- genos$Hybrid
genos$Hybrid <- NULL
genos$Hybrid$snp <- full_hybrid
genos$Hybrid$mrna <- red_hybrid
```

@@

Agronomic data for `r length(traits)` traits (including dry-matter yield (DMY))
and `r length(full_hybrid)` hybrids are available 
(Table \@ref(tab:Geno-Number)).
After applying a series of quality checks, `r ncol(snp)` SNPs and 
best linear unbiased estimates of `r ncol(mrna)` were available for further 
analyses.
Both, genomic and transcriptomic records, were collected for inbred parent lines
of `r length(red_hybrid)` hybrids.

```{r Geno-Number, echo = FALSE}
geno_tab_cap <- paste("Number of genotypes for Dent and Flint parent lines and",
                      "their hybrid progeny for which genomic and/or",
                      "transcriptomic data are available.",
                      "All genotypes for which transcriptomic data are", 
                      "available, also have genomic data.",
                      "Agronomic data are available for all 1,521 hybrid",
                      "genotypes.")
# Number of genotypes for either SNPs or mRNAs separated by hybrids and their
# parental Dent and Flint lines, respectively.
genos %>% 
  at_depth(.depth = 2, .f = length) %>%
  bind_rows() %>%
  dplyr::select(-agro) %>%
  mutate(Type = names(genos)) %>%
  dplyr::select(Type, snp, mrna) %>%
  rename("Genomic Data" = snp,
         "Transcriptomic Data" = mrna) %>%
  knitr::kable(caption = geno_tab_cap, booktabs = TRUE)
```

>>>>

knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6,
                      warning = FALSE, echo = FALSE)
```

@@

full_hybrid <- genos %>%
  filter(Pool == "Hybrid") %>%
  .$G
all_pheno <- pheno %>%
  rename(Observed = EST) %>%
  as_data_frame() %>%
  filter(G %in% full_hybrid) %>%
  dplyr::select(G, Observed, Trait) %>%
  filter(Trait != "ADL") %>%
  mutate(Trait = fct_recode(Trait, 
    "FAT" = "FETT",
    "DMY" = "GTM",
    "DMC" = "GTS",
    "PRO" = "RPR",
    "SUG" = "XZ"),
         Trait = fct_relevel(Trait, 
    c("DMY", "DMC", "ADF", "FAT", "PRO", "STA", "SUG")
    ))
traits <- all_pheno %>%
  .$Trait %>%
  levels()

# Hybrids of parents with records for both endophenotypes
red_inbreds <- genos %>% 
  filter(Pool != "Hybrid", Data_Type %in% c("snp", "mrna")) %>%
  split(.$Pool) %>%
  map(~split(., .$Data_Type)) %>%
  at_depth(.depth = 2, "G") %>%
  map(function(x) intersect(x$mrna, x$snp))

red_hybrid <- full_hybrid %>%
  as_data_frame() %>%
  separate(value, into = c("DF", "Dent", "Flint")) %>%
  mutate(Avail_Dent = ifelse(Dent %in% red_inbreds$Dent, yes = 1, no = 0),
         Avail_Flint = ifelse(Flint %in% red_inbreds$Flint, yes = 1, no = 0),
         Tested_Parents = Avail_Dent + Avail_Flint) %>%
  filter(Tested_Parents == 2) %>%
  unite(Hybrid, DF, Dent, Flint) %>%
  .$Hybrid
genos <- genos %>%
  rbind(tibble(G = red_hybrid,
               Pool = "Hybrid",
               Data_Type = "mrna")
        )
```

@@

Agronomic data for `r length(traits)` traits (including dry-matter yield (DMY))
and `r length(full_hybrid)` hybrids are available 
(Table \@ref(tab:Geno-Number)).
After applying a series of quality checks, `r ncol(snp)` SNPs and 
best linear unbiased estimates of `r ncol(mrna)` were available for further 
analyses.
Genomic, pedigree and transcriptomic records, were collected for inbred parent 
lines of `r length(red_hybrid)` hybrids.

```{r Geno-Number, echo = FALSE}
geno_tab_cap <- paste("Number of genotypes for Dent and Flint parent lines and",
                      "their hybrid progeny for which genomic and/or",
                      "transcriptomic data are available.",
                      "All genotypes for which transcriptomic data are", 
                      "available, also have genomic data.",
                      "Agronomic data are available for all 1,521 hybrid",
                      "genotypes.")
# Number of genotypes for either SNPs or mRNAs separated by hybrids and their
# parental Dent and Flint lines, respectively.
genos %>% 
  mutate(Data_Type = fct_recode(Data_Type,
                                Agronomic = "agro",
                                Transcriptomic = "mrna",
                                Genomic = "snp",
                                Pedigree = "ped")) %>%
  group_by(Pool, Data_Type) %>%
  count() %>%
  rename(`Data Type` = Data_Type) %>%
  knitr::kable(caption = geno_tab_cap, booktabs = TRUE)
```

### 2016-10-21 reports/impute_single_mrna.Rmd
remove code boxes from report

# Genotype-Wise mRNA-Imputation

## Function for the imputation of a single mRNA.
```{r Impute-mRNA-Function}
## Function for the imputation of a single mRNA
impute_one_mrna <- function(x, y) {
  geno <- rownames(x)
  # Names of genotypes for which transcriptomic records exist
  nm2 <- rownames(y)
  # Names of genotypes for which transcriptomic records are missing.
  nm1 <- setdiff(rownames(x), nm2)
  # Hybrid parents not in y.
  geno1 <- geno[geno %in% nm1]
  # Hybrid parents in y.
  geno2 <- geno[geno %in% nm2]
  x <- x[match(unique(geno), rownames(x)), ]
  # Design matrix mapping GCA effects from genotypes with transcriptomic
  # records to y2.
  Z2 <- Matrix::sparse.model.matrix(~-1 + factor(geno2),
                                    drop.unused.levels = FALSE)
  colnames(Z2) <- gsub("factor\\(geno2\\)", replacement = "", x = colnames(Z2))
  Z2 <- Z2[, match(nm2, colnames(Z2))]
  rownames(Z2) <- geno2
  # Hybrid parents not in y.
  geno1 <- geno[geno %in% nm1]
  # Hybrid parents in y.
  geno2 <- geno[geno %in% nm2]
  x <- x[match(unique(geno), rownames(x)), ]
  y <- y[nm2, ]
  M2 <- y[, matrixStats::colVars(y) != 0]
  x <- x[, matrixStats::colVars(x) != 0]
  A <- build_kernel(M = x, lambda = 0.01, algorithm = "RadenII")
  A11 <- A[nm1, nm1, drop = FALSE]
  A12 <- A[nm1, nm2, drop = FALSE]
  A21 <- A[nm2, nm1, drop = FALSE]
  A22 <- A[nm2, nm2, drop = FALSE]
  Ainv <- solve(A)
  dimnames(Ainv) <- dimnames(A)
  A_up11 <- Ainv[nm1, nm1]
  A_up12 <- Ainv[nm1, nm2]
  # Eq.21
  M1 <- A12 %*% solve(A22) %*% M2
  J2 <- matrix(-1, nrow = ncol(A12), ncol = 1)
  # Eq.22
  J1 <- A12 %*% solve(A22) %*% J2
  # Eq.10
  epsilon <- t(chol(solve(Ainv[nm1, nm1])))
  # Eq.20
  W2 <- Z2 %*% M2
  w1 <- A12 %*% solve(A22) %*% Z2 %*% M2
  as.numeric(w1)
}
```

Plot the distribution of correlations between vectors of original and imputed
mRNAs.
```{r Correlation-Imputed-vs-NonImputed}
#imp_mrna <- vapply(seq_len(nrow(y)), FUN = function(i) {
#  z <- y[-i, ]
#  imp_mrna <- impute_one_mrna(x, z)
#  cor(y[i, ], imp_mrna)
#}, FUN.VALUE = numeric(1))
#hist(imp_mrna)
```

>>>>

# Genotype-Wise mRNA-Imputation
```{r echo = FALSE}
pacman::p_load("sspredr", "tidyverse", "caret", "e1071", "viridis",
               "forcats", "knitr", "rmarkdown", "purrr", "rprojroot",
               "methods", "parallel")
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ".", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, 
                      warning = FALSE, message = FALSE, echo = FALSE)
```

```{r Predictor-Data, cache = TRUE}
# Common genotypes
genos <- readRDS("./data/processed/common_genotypes.RDS")
mrna_inbreds <- genos %>%
  filter(Data_Type == "mrna") %>%
  split(.$Pool) %>%
  map("G")

# Remove the 'Group' variable after splitting Dent and Flint data.
rm_grp <- function(x) {
  x$Group <- NULL
  x
}

# mRNA
mrna <- readRDS("./data/processed/subset_mrna_blues.RDS")[["100%"]]
mrna <- t(mrna)
mrna <- mrna[grep("Exp|Sigma", x = rownames(mrna), invert = TRUE), ]
mrna_lst <- mrna %>%
  as_data_frame() %>%
  mutate(G = rownames(mrna)) %>%
  mutate(Group = ifelse(G %in% mrna_inbreds$Dent, yes = "Dent", no = "Flint"),
         Group = as.factor(Group)) %>%
  as.data.frame() %>%
  column_to_rownames(var = "G") %>%
  split(.$Group) %>%
  map(rm_grp) %>%
  map(~as.matrix(.))

# SNPs
snp <- readRDS("./data/processed/snp_mat.RDS")
snp_lst <- snp %>%
  as_data_frame() %>%
  mutate(G = rownames(snp)) %>%
  filter(G %in% (mrna_inbreds %>% flatten_chr())) %>%
  mutate(Group = ifelse(G %in% mrna_inbreds$Dent, yes = "Dent", no = "Flint"),
         Group = as.factor(Group)) %>%
  as.data.frame() %>%
  column_to_rownames(var = "G") %>%
  split(.$Group) %>%
  map(rm_grp) %>%
  map(~as.matrix(.))

# Pedigree
ped <- readRDS("./data/processed/ped-datafull-GTP.RDS")
ped_lst <- ped %>%
  mutate(G = rownames(ped)) %>%
  filter(G %in% (mrna_inbreds %>% flatten_chr())) %>%
  mutate(Group = ifelse(G %in% mrna_inbreds$Dent, yes = "Dent", no = "Flint"),
         Group = as.factor(Group)) %>%
  as.data.frame() %>%
  column_to_rownames(var = "G") %>%
  split(.$Group) %>%
  map(rm_grp) %>%
  map(as.matrix) %>%
  map(function(x) x[, match(rownames(x), colnames(x))]) %>%
  map(function(x) x * 2) %>%
  map(function(x) {
    x[is.na(x)] <- 0
    x
  })
```

```{r Impute-mRNA-Function}
## Function for the imputation of a single mRNA
impute_mrna_genotype <- function(x, y) {
  geno <- rownames(x)
  # Names of genotypes for which transcriptomic records exist
  nm2 <- rownames(y)
  # Names of genotypes for which transcriptomic records are missing.
  nm1 <- setdiff(rownames(x), nm2)
  # Hybrid parents not in y.
  geno1 <- geno[geno %in% nm1]
  # Hybrid parents in y.
  geno2 <- geno[geno %in% nm2]
  x <- x[match(unique(geno), rownames(x)), ]
  # Design matrix mapping GCA effects from genotypes with transcriptomic
  # records to y2.
  Z2 <- Matrix::sparse.model.matrix(~-1 + factor(geno2),
                                    drop.unused.levels = FALSE)
  colnames(Z2) <- gsub("factor\\(geno2\\)", replacement = "", x = colnames(Z2))
  Z2 <- Z2[, match(nm2, colnames(Z2))]
  rownames(Z2) <- geno2
  # Hybrid parents not in y.
  geno1 <- geno[geno %in% nm1]
  # Hybrid parents in y.
  geno2 <- geno[geno %in% nm2]
  x <- x[match(unique(geno), rownames(x)), ]
  y <- y[nm2, ]
  M2 <- y[, matrixStats::colVars(y) != 0]
  x <- x[, matrixStats::colVars(x) != 0]
  A <- build_kernel(M = x, lambda = 0.01, algorithm = "RadenII")
  A11 <- A[nm1, nm1, drop = FALSE]
  A12 <- A[nm1, nm2, drop = FALSE]
  A21 <- A[nm2, nm1, drop = FALSE]
  A22 <- A[nm2, nm2, drop = FALSE]
  Ainv <- solve(A)
  dimnames(Ainv) <- dimnames(A)
  A_up11 <- Ainv[nm1, nm1]
  A_up12 <- Ainv[nm1, nm2]
  # Eq.21
  M1 <- A12 %*% solve(A22) %*% M2
  J2 <- matrix(-1, nrow = ncol(A12), ncol = 1)
  # Eq.22
  J1 <- A12 %*% solve(A22) %*% J2
  # Eq.10
  epsilon <- t(chol(solve(Ainv[nm1, nm1])))
  # Eq.20
  W2 <- Z2 %*% M2
  w1 <- A12 %*% solve(A22) %*% Z2 %*% M2
  as.matrix(w1)
}

# Shuffled version of the imputation function above.
shuffled_imputation <- function(x, y) {
  cor_lst <- lapply(seq(from = 1, to = nrow(y) - 2), FUN = function(i) {
    idx <- sample(nrow(y), size = i, replace = FALSE)
    z <- y[-idx, ]
    imp_mrna <- impute_mrna_genotype(x = x, y = z)
    orig_mrna <- y[match(rownames(imp_mrna), rownames(y)), , drop = FALSE]
    stopifnot(identical(rownames(imp_mrna), rownames(orig_mrna)))
    cor(c(imp_mrna), c(orig_mrna))
  })
  cor_lst %>%
    flatten_dbl() %>%
    tbl_df() %>%
    rownames_to_column(var = "Number_NA_Geno") %>%
    rename(Value = value)
}
```

## Correlations between vectors of original and imputed mRNAs.
### General idea:
*    Impute transcriptomic data for different numbers of genotypes (from 1 to
     number of genotypes with transcriptomic data).
*    For each number of genotypes without transcriptomic data, randomly sample 
     1000 sets of genotypes, which will be imputed.
     This will allow us to aggregate and summarize the correlation between 
     observed and imputed mRNAs with high confidence.

The computations were run using multiple cores with 
[this script](../analysis/impute_single_mrna.R).
```{r Shuffle-Genotypes-Correlate-Imputation, eval = FALSE}
repl <- 1000
donors <- c("snp_lst", "ped_lst")
imp_lst <- lapply(donors, FUN = function(type) {
  par_lst <- vector(mode = "list", length = repl)
  names(par_lst) <- paste0("Replication_", seq_len(repl))
  par_lst[] <- mclapply(par_lst, FUN = function(iter, ...) {
    try(map2(.x = get(type), .y = mrna_lst, .f = shuffled_imputation))
  }, mc.cores = use_cores)
  par_lst
})
names(imp_lst) <- donors
```

```{r Plot-Correlation-Imputed-vs-NonImputed, cache = TRUE, fig.width = 12, fig.height = 12, fig.cap = "Pearson correlation coefficients between original and imputed mRNA genotypes for two heterotic groups and two sources of information (i.e. genomic and pedigree)."}
par_lst <- readRDS("./data/derived/impute_single_mrna.RDS")
par_lst %>%
  map(~keep(., is_list)) %>%
  at_depth(.depth = 2, ~bind_rows(., .id = "Group")) %>%
  map(~bind_rows(., .id = "Replication")) %>%
  bind_rows(.id = "Data_Type") %>%
  mutate(Data_Type = fct_recode(Data_Type,
                                Genomic = "snp_lst",
                                Pedigree = "ped_lst")) %>%
  mutate(Number_NA_Geno = as.factor(Number_NA_Geno)) %>%
  mutate(Number_NA_Geno = fct_inorder(Number_NA_Geno)) %>%
  ggplot(aes(x = Number_NA_Geno, y = Value)) +
  geom_boxplot() +
  facet_wrap(Data_Type ~ Group) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) +
  xlab("Number of Genotypes Without mRNA-Data") +
  ylab("Correlation Between Original and Imputed mRNA BLUEs")
```

### 2016-10-21 reports/intro.Rmd
remove code boxes from report

---
output: pdf_document
---
# Introduction
The integration of different sources of information for the prediction of 
breeding or production values is one of the major challenges in current genomic 
prediction research.
In the early years of genomic prediction, a 2-step procedure was the most 
intuitive choice for establishing a new selection scheme.
The first consists of conventionally estimating breeding values based on 
pedigree relationships and therefore the phenotypes of relatives.
Individuals with accurate breeding values out of the first step (i.e. high 
number of offspring), enter the second step in which SNP genotypes are regressed 
against the conventional breeding values.
Those markers can then be used to predict genomic breeding values for solely 
genotyped and potentially very young individuals.
Considering the two sources of information &mdash; pedigree and high density SNP 
genotypes &mdash; the process can be described as follows:

>>>>

# Introduction
The integration of different sources of information for the prediction of 
breeding or production values is one of the major challenges in current genomic 
prediction research.
In the early years of genomic prediction, a 2-step procedure was the most 
intuitive choice for establishing a new selection scheme.
The first consists of conventionally estimating breeding values based on 
pedigree relationships and therefore the phenotypes of relatives.
Individuals with accurate breeding values out of the first step (i.e. high 
number of offspring), enter the second step in which SNP genotypes are regressed 
against the conventional breeding values.
Those markers can then be used to predict genomic breeding values for solely 
genotyped and potentially very young individuals.
Considering the two sources of information &mdash; pedigree and high density SNP 
genotypes &mdash; the process can be described as follows:

### 2016-10-21 reports/loocv_issues.Rmd
remove code boxes from report

Meine Annahme ist, dass die effiziente Implementierung von LOOCV (Cheng et al.,
2016) den gesamten Stichprobenumfang (mit Ausnahme der einen Hybride im test 
set) als training set nutzt.
Allerdings wollen wir LOOCV ja nur auf T0-Hybride anwenden.
In diesem Fall kann nicht jede Hybride, die zuvor Teil des training sets fuer 
die Vorhersage einer anderen Hybride war, vom training in das test set 
ueberfuehrt werden.
Ich habe das nachfolgend mal anhand eines kleinen Beispiels illustriert:

|:---:|:----:|
|ID   |Hybride|
|1    |Aa     |
|2    |Ab     |
|3    |Ac     |
|4    |Ba     |
|5    |Bb     |
|6    |Bc     |
|7    |Ca     |
|8    |Cb     |
|9    |Cc     |

: Hybride und ihre korrespondierenden IDs.

@@

: Hybride im test set und korrespondierende T0-Hybride im training set. Die Hybride sind mit ihren IDs aus der vorherigen Tabelle gekennzeichnet.

Hybride \#1 kann mit den Hybriden 5, 6, 8 und 9 vorhergesagt werden, aber die
Hybride \#5 kann nicht mit den Hybriden 6 und 8 vorhergesagt werden, Hybride 
\#6 kann nicht mit den Hybriden 5, 6 und 9 vorhergesagt werden, Hybride \#8 
kann nicht mit den Hybriden 5 und 9 vorhergesagt werden, und Hybride \#9 kann 
nicht mit den Hybriden 6 und 8 vorhergesagt werden.

>>>>

My assumption is that the efficient implementation of LOOCV proposed by Cheng
et al. (2016) uses the entire sample space except for a single hybrid that 
is used as a test set.
However, our goal is to apply LOOCV only to the T0 hybrids.
In this case, not very hybrid, that was previously part of the training set to
predict another hybrid, can be moved to the test set (see the following 
example).

|:---:|:----:|
|ID   |Hybrid|
|1    |Aa    |
|2    |Ab    |
|3    |Ac    |
|4    |Ba    |
|5    |Bb    |
|6    |Bc    |
|7    |Ca    |
|8    |Cb    |
|9    |Cc    |

: Hybrids and their corresponding IDs.

@@

: Hybrids in the test set and their corresponding T0-Hybrids in the training 
set. The hybrids are denoted by their IDs from the previous table.

Hybrid \#1 can be predicted with hybrids 5, 6, 8 and 9, however, hybrid \#5 
cannot be predicted with hybrids 6 and 8, hybrid \#6 cannot be predicted with 
hybrids 5, 6 and 9, hybrid \#8 cannot be predicted with hybrids 5 and 9, and 
hybrid \#9 cannot be predicted with hybrids 6 und 8.

## Proposed Solution

### 2016-10-21 reports/loocv_reduced.Rmd
remove code boxes from report

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = "~/gamazon/",
                     inline = TRUE,
                     verbose = FALSE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 6,
                      warning = FALSE, echo = FALSE)
```

@@

```{r Rename-Traits, cache = TRUE}
loocv_clean <- loocv %>%
  mutate(Trait = fct_recode(Trait, 
                            "FAT" = "FETT",
                            "PRO" = "RPR",
                            "DMY" = "GTM",
                            "DMC" = "GTS",
                            "SUG" = "XZ"),
         Trait = fct_relevel(Trait, c("DMY", "DMC", "ADF", "FAT", "PRO", "STA",
                                      "SUG")),
         Dent_NA_Fraction = as.factor(as.character(Dent_NA_Fraction)),
         Flint_NA_Fraction = as.factor(as.character(Flint_NA_Fraction)),
         Residuals = y - yhat,
         Predictor = fct_recode(Predictor,
                                "mRNA" = "mrna",
                                "SNP" = "snp")
  )
```

@@

## Predictive Ability for 'Full' vs 'Reduced' Data
```{r Non-Imputed-Pred-Ability, cache = TRUE}
loocv_tbl_cap <- paste("Predictive abilities for the 'reduced' set of hybrids",
                       "using two different predictors and seven agronomic",
                       "traits. Results are ranked by predictive ability.")
pred_reduced <- loocv_clean %>%
  filter(Dent_NA_Fraction == 0, Flint_NA_Fraction == 0) %>%
  mutate(Predictor = as.factor(Predictor)) %>%
  droplevels() %>%
  group_by(Predictor, Trait) %>%
  summarize(Pred_Ability = round(cor(y, yhat), digits = 2)) %>%
  spread(key = "Predictor", value = "Pred_Ability") %>%
  rename(Reduced_mRNA = mRNA,
         Reduced_SNP = SNP)
```

@@

full_loocv_clean <- full_loocv %>%
  mutate(Trait = as.factor(Trait),
         Trait = fct_recode(Trait, 
                            "FAT" = "FETT",
                            "PRO" = "RPR",
                            "DMY" = "GTM",
                            "DMC" = "GTS",
                            "SUG" = "XZ"),
         Trait = fct_relevel(Trait, c("DMY", "DMC", "ADF", "FAT", "PRO", "STA",
                                      "SUG")),
         Residuals = y - yhat,
         Predictor = as.factor(as.character(Imputation)),
         Predictor = fct_recode(Predictor,
                                "mRNA" = "TRUE",
                                "SNP" = "FALSE")
  )
full_loocv_tbl_cap <- paste(
  "Predictive abilities for the 'full' and the 'reduced' set of hybrids using",
  "two different predictors and seven agronomic traits."
  )
full_loocv_clean %>%
  droplevels() %>%
  group_by(Predictor, Trait) %>%
  summarize(Pred_Ability = round(cor(y, yhat), digits = 2)) %>%
  spread(key = "Predictor", value = "Pred_Ability") %>%
  rename(Full_mRNA = mRNA,
         Full_SNP = SNP) %>%
  full_join(y = pred_reduced, by = "Trait") %>%
  knitr::kable(caption = full_loocv_tbl_cap, booktabs = TRUE)
```

>>>>

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6,
                      warning = FALSE, echo = FALSE)
```

@@

```{r Rename-Traits, cache = TRUE}
loocv_clean <- loocv %>%
  mutate(Trait = fct_recode(Trait, 
                            "FAT" = "FETT",
                            "PRO" = "RPR",
                            "DMY" = "GTM",
                            "DMC" = "GTS",
                            "SUG" = "XZ"),
         Trait = fct_relevel(Trait, c("DMY", "DMC", "ADF", "FAT", "PRO", "STA",
                                      "SUG")),
         Dent_NA_Fraction = as.factor(as.character(Dent_NA_Fraction)),
         Flint_NA_Fraction = as.factor(as.character(Flint_NA_Fraction)),
         Residuals = y - yhat,
         Predictor = fct_recode(Predictor,
                                "Transcriptomic" = "mrna",
                                "Genomic" = "snp")
  )
```

@@

## Predictive Ability for 'Full' vs 'Reduced' Data
```{r Non-Imputed-Pred-Ability, cache = TRUE}
loocv_tbl_cap <- paste("Predictive abilities for the 'reduced' set of hybrids",
                       "using two different predictors and seven agronomic",
                       "traits. Results are ranked by predictive ability.")
pred_reduced <- loocv_clean %>%
  filter(Dent_NA_Fraction == 0, Flint_NA_Fraction == 0) %>%
  mutate(Predictor = as.factor(Predictor)) %>%
  droplevels() %>%
  group_by(Predictor, Trait) %>%
  summarize(Pred_Ability = round(cor(y, yhat), digits = 2)) %>%
  spread(key = "Predictor", value = "Pred_Ability") %>%
  rename(Reduced_Transcriptomic = Transcriptomic,
         Reduced_Genomic = Genomic)
```

@@

full_loocv_clean <- full_loocv %>%
  mutate(Trait = as.factor(Trait),
         Trait = fct_recode(Trait, 
                            "FAT" = "FETT",
                            "PRO" = "RPR",
                            "DMY" = "GTM",
                            "DMC" = "GTS",
                            "SUG" = "XZ"),
         Trait = fct_relevel(Trait, c("DMY", "DMC", "ADF", "FAT", "PRO", "STA",
                                      "SUG")),
         Residuals = y - yhat,
         Predictor = as.factor(as.character(Imputation)),
         Predictor = fct_recode(Predictor,
                                "Transcriptomic" = "TRUE",
                                "Genomic" = "FALSE")
  )
full_loocv_tbl_cap <- paste(
  "Predictive abilities for the 'full' and the 'reduced' set of hybrids using",
  "two different predictors and seven agronomic traits."
  )
full_loocv_clean %>%
  droplevels() %>%
  group_by(Predictor, Trait) %>%
  summarize(Pred_Ability = round(cor(y, yhat), digits = 2)) %>%
  spread(key = "Predictor", value = "Pred_Ability") %>%
  rename(Full_Transcriptomic = Transcriptomic,
         Full_Genomic = Genomic) %>%
  full_join(y = pred_reduced, by = "Trait") %>%
  knitr::kable(caption = full_loocv_tbl_cap, booktabs = TRUE)
```
